---
title: "Jinbin Xu Putamen"
############################################################
# Author Guoyan Zhao                                       #
# Department of Neuroscience                               #
# gzhao@wustl.edu                                          #
# Copyright (C) 2019 Washington University, St. Louis, MO. #
# All Rights Reserved.                                     #
############################################################

output:
  html_document:
    theme: united
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'
---
***

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  cache.lazy = FALSE,
  tidy = TRUE
)
```
setwd("C:/gzhao/Labs/Jinbin_Xu_Putamen/Putamen_S2_CleanObject/")

### Setup the Seurat Object
```{r init, message=FALSE}
library(Seurat)
library(sctransform)
library(RColorBrewer) # colorRampPalette(), brewer.pal
library(ggplot2) # qplot(), position_nudge(), geom_text()
library(cowplot) # for plot_grid
library(gplots) # for heatmap2
```

```{}
# Load the dataset
data_original <- readRDS( file = "C:/gzhao/Labs/Jinbin_Xu_Putamen/Putamen_S1_createObj/ Putamen_S1_CreateObject_dim20_res0.15_obj_cleaned.rds", refhook = NULL)
```

```{}
obj.list <- SplitObject(data_original, split.by = "orig.ident")

for (i in 1:length(obj.list)) {
    obj.list[[i]] <- SCTransform(obj.list[[i]],  vars.to.regress = c("nCount_RNA", "percent.mt"),verbose = FALSE)
}

#adjust max memory for global environment
options(future.globals.maxSize= 53687091200)

###integrate data
alldata.features <- SelectIntegrationFeatures(object.list = obj.list, nfeatures = 3000)
alldata_prepsct <- PrepSCTIntegration(object.list = obj.list, anchor.features = alldata.features, verbose = FALSE)
alldata.anchors <- FindIntegrationAnchors(object.list = alldata_prepsct, normalization.method = "SCT", anchor.features = alldata.features, verbose = FALSE)
data_integrated <- IntegrateData(anchorset = alldata.anchors, normalization.method = "SCT", verbose = FALSE)

data_integrated <- RunPCA(data_integrated,  npcs = 30)

#set dims parameter
dims=1:20
data_integrated <- RunUMAP(data_integrated, reduction = "pca", dims = dims)
data_integrated <- FindNeighbors(data_integrated, reduction = "pca", dims = dims)
data_integrated <- FindClusters(data_integrated, resolution = 0.1)

# Visualization
p1 <- DimPlot(data_integrated, reduction = "umap", group.by = "orig.ident")
p2 <- DimPlot(data_integrated, reduction = "umap", label = TRUE)

png("Putamen_cleanObj_dim20_res0.1_CellCluster.png",    
  width = 12*300,        # 5 x 300 pixels
  height = 5*300,
  res = 300,            # 300 pixels per inch
  pointsize = 8)        # smaller font size
    plot_grid(p1, p2)
dev.off()
```
# find conserved marker gene for each cluster
DefaultAssay(data_integrated) <- "SCT"

Conserved_cluster_markers <- list() # list starting subscript is 1, can't use 0
for (i in 0:(nlevels(data_integrated@active.ident)-1)) {
  Conserved_cluster_markers[[i+1]] <- FindConservedMarkers(data_integrated, assay = "SCT", slot = "data", test.use = "wilcox", min.pct = 0.2, ident.1 = i, grouping.var = "Genotype", verbose = FALSE, only.pos = TRUE)
}

```{}
DefaultAssay(data_integrated) <- "RNA"

# Normalize RNA data for visualization purposes
data_integrated <- NormalizeData(data_integrated, verbose = FALSE)

# plot marker genes 3x4
marker_genes <- c( "AQP4", "RGS5", "PTPRC", "SYT1", "PLP1", "MEGF11")

png("Putamen_cleanObj_dim20_res0.1_Marker_FeaturePlot.png",      
    width = 16*300,        # 5 x 300 pixels
    height = 10*300,
    res = 300,            # 300 pixels per inch
    pointsize = 5)        # smaller font size

FeaturePlot(data_integrated, features = marker_genes, min.cutoff = "q9", max.cutoff = "q95", ncol = 4)
dev.off()
# use "no.legend = FALSE" to add ledgend

# Violin plot
png("Putamen_cleanObj_dim20_res0.1_Marker_VlnPlot_FigS1.png",      
    width = 11*300,        # 5 x 300 pixels
    height = 8*300,
    res = 300,            # 300 pixels per inch
    pointsize = 5)        # smaller font size
VlnPlot(data_integrated, assay = "RNA", features = marker_genes) 
dev.off()
```

# subset clusters and write the object out
```{r subset cess from Granule cell cluster for further analysis}
saveRDS(data_integrated, file = "Putamen_cleanObj_dim20_res0.1.rds")

# Oligodendrocyte
subcluster <- subset(data_integrated, idents  = c("0"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter0_Oligodendrocyte.rds")

# Astrocyte
subcluster <- subset(data_integrated, idents  = c("2"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter2_Astrocyte.rds")

# Hematopoietic
subcluster <- subset(data_integrated, idents  = c("4"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter4_HematopoieticMicroglia.rds")

# EndotheliaPericypte
subcluster <- subset(data_integrated, idents  = c("5"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter5_EndotheliaPericyte.rds")

# OPC
subcluster <- subset(data_integrated, idents  = c("6"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter6_OPC.rds")

# cluster 10 is novel with many novel markers. Express astrocyte markers at lower
# levels, have very few cells, 
subcluster <- subset(data_integrated, idents  = c("10"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter10_Unknown.rds")

# neurons
subcluster <- subset(data_integrated, idents  = c("1", "3", "7", "8", "9", "11"))
saveRDS(subcluster, file = "Putamen_cleanObj_dim20_res0.1_cluter1_3_7_8_9_11_Neuron.rds")

```

```{}
# save workspace
save.image("Putamen_S2_cleanObj_dim20_res0.1.RData")
